Video Understanding : A review of action detection-recognition dataset

### 2024-01-19 conference_101719.tex
origin

\section{Introduction}
In the past decade, deep learning models have achieved remarkable success and have outperformed traditional methods in various tasks, including object detection, sound source separation, action recognition, and more. Currently, there is an increasing number of research studies being conducted to apply and improve existing models or create new architectures to address real-world problems. The rapid success of deep learning models can largely be attributed to two factors: the advancement of computer hardware in terms of computational power and memory capacity, as well as the expanding scale of available datasets.

\textbf{Advancement of computer hardware} :

\begin{center}
	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
	\caption{Example of a figure caption.}
	\label{SSD300} 
\end{center}

>>>>

\section{Introduction}
In the past decade, deep learning models have achieved remarkable success and have outperformed traditional methods in various tasks, including object detection, sound source separation, action recognition, and more. Currently, there is an increasing number of research studies being conducted to apply and improve existing models or create new architectures to address real-world problems. Deep learning models require powerful computational capabilities, which are easily achieved in a laboratory environment but challenging to deploy in real-world settings. However, the rapid development of computer hardware has increasingly facilitated the practical application of deep learning models, opening up opportunities for computationally intensive and real-time tasks such as video understanding, with action detection and recognition being the most prominent among them.

For video understanding tasks such as action detection and action recognition, besides the requirement for significant computational resources, they also demand a large and sufficiently complex dataset. In addition to serving as training data, datasets also provide a portion of data specifically for evaluating models, thereby establishing a common benchmark for comparing different models. Over the years, new datasets have emerged, either as additions to existing datasets or as entirely new ones based on different construction perspectives. This has increased both the diversity and quantity of available data, but also inadvertently posed challenges in selecting an appropriate dataset. Evaluating whether a dataset is suitable for a given research problem is not merely a matter of its scale. Other characteristics must also be considered, such as the dataset creator's perspective, data collection methods, sample size, number of classes, level of annotation detail (spatial, temporal, sound, etc.), popularity within the research community, the baseline for comparison, and various other factors. Therefore, it is necessary to carefully examine datasets relevant to the task, gather information, evaluate, and then compare them to ultimately select the desired dataset for research purposes. This process typically consumes a significant amount of time and effort. To address this issue, in this paper, we aim to compile notable datasets in the fields of action detection and action recognition, listing them chronologically while providing concise necessary information regarding:

\begin{itemize}
	\item \textit{Context and construction perspective of the dataset}: Since the datasets are presented chronologically, this section clarifies the information regarding the background and the authors' perspectives on the shortcomings or the necessary additions to older datasets.
	\item \textit{Dataset distribution}: Information about the dataset, such as the number of data samples, the number of classes, the train-validation splits, and any other available details.
	\item \textit{Annotations}: Explanation of the annotations provided in the dataset.
	\item \textit{Data collection methods}: We summarize the data collection process employed by the respective author groups on that dataset. This allows for a more objective assessment of the dataset's reliability and quality based on the researcher's perspective.
\end{itemize}

In the next section, we will list the datasets in the order of their publication time (measured from the time the accompanying paper is published). Each dataset will include four pieces of information presented in the following order: "Context and Construction Perspective of the Dataset," "Annotations," "Dataset Distribution," and "Data Collection Methods." If some information is not provided by the authors in the original paper, it will be left blank or omitted. Additionally, if the authors provide any additional information included in the dataset, we will allocate a separate section below to describe it. The list of datasets, along with a brief overview of their publication dates and the mentioned data quantities, can be found in Fig1..
